\pagebreak

\cvsection{Presentations}

\begin{cventries}
  \cventry
    {} % Job title
    {Oral - Invited} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Molecular Dynamics Simulations of Biological Systems: Enzyme Conformational Change and Small Molecule (DNA) Sequencing}, Southeastern LA Univ. Chemistry \& Physics Seminar (2010). In \textit{Southeastern LA Univ. Chemistry \& Physics Seminar}; 2010.}
      \end{cvitems}
    }
    
  \cventry
    {} % Job title
    {Oral - Conference} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} 
        \item {\textbf{Molecular Simulation of Single Nucleotides Moving through Nanoslits Composed of Self-Assembled Monolayers Terminated with Various Chemical Groups}. Tong, X.; Novak, B.; Moldovan, D. In \textit{ACS Spring National Meeting}; 2018.}
        \item {\textbf{Properties of Liquid Ti Alloys from Electrostatic Levitation Experiments and Simulation}. Novak, B.; Raush, J.; Zhang, X.; Moldovan, D.; Meng, W.; Guo, S. In \textit{APS March Meeting}; 2017.}
        \item {\textbf{Self-Assembly of Linear Peptide Analogs and Their Interaction with Lipid Bilayers Using MD Simulations}. In Novak, B.; Moldovan, D. \textit{89th ACS Colloid \& Surface Science Symposium}; 2015.}
        \item {\textbf{MD Simulations of Cationic Linear Peptide Analogs: Self-Assembly and Interaction with DPPC and DPPC/DPPS Lipid Bilayers}. Novak, B. R.; Lin, J.; Moldovan, D. In \textit{ACS Fall National Meeting}; 2014.}
        \item {\textbf{Interaction of Cationic Linear Peptide Analogs with Negatively Charged Lipid Bilayers Studied with Molecular Dynamics Simulations}. Novak, B. R.; Lin, J.; Moldovan, D. In \textit{ACS Spring National Meeting}; 2013.}
        \item {\textbf{Interaction of PLGA nanoparticles with a DMPC bilayer studied using molecular dynamics simulations.} Novak, B.; Astete, C.; Sabliov, C.; Moldovan, D. In APS March Meeting; 2012.}
        \item {\textbf{Simulations of Single DNA Nucleotide Transport Through Nanoslits}. Novak, B.; Xia, K.; Moldovan, D.; Nikitopoulos, D.; Soper, S. In \textit{APS March Meeting}; 2011.}
        \item {\textbf{Opening/Closing Dynamics and Subunit Communication in Biotin Carboxylase}. Novak, B.; Moldovan, D.; Waldrop, G. L.; de Queiroz, M. S. In \textit{Southwest \& Southeastern Regional Meeting of the ACS}; 2010.}
        \item {\textbf{Molecular Dynamics Simulations of the Transport of Single DNA Nucleotides Through Nanochannels}. Novak, B.; Moldovan, D.; Nikitopoulos, D.; Soper, S. In \textit{APS March Meeting}; 2010.}
        \item{\textbf{Applying a Thermodynamic Model to Predict the Size of Surface Indentations That Affect Bubble Nucleation}. Novak, B.; Maginn, E. J.; McCready, M. J. In \textit{AIChE Annual Meeting}; 2007.}
        \item {\textbf{Molecular Dynamics Investigation of Bubble Nucleation at a Solid Surface}. Novak, B.; Maginn, E. J.; McCready, M. J. In \textit{Midwest Thermodynamics and Statistical Mechanics Conference}; 2006.}
        \item {\textbf{Effects of Geometric Defects on Superheated Heterogeneous Bubble Nucleation: A Molecular Dynamics Study}. Novak, B.; Maginn, E. J.; McCready, M. J. In \textit{AIChE Annual Meeting}; 2006. }
        \item {\textbf{Superheated Homogeneous and Heterogeneous Bubble Nucleation Rates Using NPT and NP\textsubscript{zz}T Molecular Dynamics: Effects of Surface Interactions}. Novak, B.; Maginn, E. J.; McCready, M. J. In \textit{AIChE Annual Meeting}; 2005.}
      \end{cvitems}
    }
    
  \cventry
    {} % Job title
    {Poster - Conference} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {\textbf{Insights into the Opening and Closing Dynamics of Biotin Carboxylase}. Novak, B.; Moldovan, D.; Waldrop, G.; de Queiroz, M. In \textit{APS March Meeting}; 2010.}        
        \item {\textbf{Opening and Closing of Biotin Carboxylase: Free Energies and Mean First Passage Times}. Novak, B.; Moldovan, D.; Waldrop, G.; de Queiroz, M. In \textit{Mardi Gras Conference}; 2010.}
        \item {\textbf{Molecular Dynamics Simulations for Calculation of Times of Flight of Single DNA Nucleotides Driven through Nanochannels}. Novak, B.; Moldovan, D.; Nikitopoulos, D.; Soper, S. In \textit{Mardi Gras Conference}; 2010.}
        \item {\textbf{MD Simulations of DNA Mononucleotide Transport through Nanochannels}. Novak, B.; Lin, J.; Moldovan, D.; Jha, S.; Soper, S.; Nikitopoulos, D. In \textit{21st EPSCoR National Conference}; 2009.}
        \item {\textbf{Umbrella Sampling Simulations of the Closure of Biotin Carboxylase}. Novak, B.; Moldovan, D.; Waldrop, G.; de Queiroz, M. In \textit{International Conference on Multiscale Materials Modeling}; 2008.}
      \end{cvitems}
    }
    
  \cventry
    {} % Job title
    {Author only} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Molecular Dynamics Simulation Study of the Effect of Lignin Dimers on the Gel to Liquid-Crystalline Transition Temperature in DPPC Bilayers}. Tong, X.; Maradipour, M.; Novak, B.; Knutson, B.; Rankin, S.; Lynn, B.; Moldovan, D. In \textit{ACS Spring National Meeting}; 2019.}
        \item {\textbf{Phase Field Modeling of Rapid Solidification of Ti-Ni Alloy Parameterized Using Interfacial Properties Calculated from Atomistic Simulations}. Kavousi, S.; Novak, B.; Moldovan, D. In \textit{MRS Fall Meeting}; 2019.}
        \item {\textbf{Combined Molecular Dynamics and Phase Field Simulation Study of Directional Solidification of NiTi Alloy}. Kavousi, S.; Novak, B.; Moldovan, D. In \textit{TMS Annual Meeting \& Exhibition}; 2019.}
        \item {\textbf{Molecular Dynamics Simulation Study of Alpha-Tocopherol Interaction with Lipid Bilayers}. Kavousi, S.; Novak, B.; Moldovan, D. In \textit{ACS Spring National Meeting}; 2018.}
        \item {\textbf{Ab Initio Calculations of Transport in Titanium and Aluminum Mixtures}. Walker, N.; Novak, B.; Tam, K. M.; Moldovan, D.; Jarrell, M. In \textit{APS March Meetin}g; 2017.}
        \item {\textbf{Finite Size Scaling of the First Order Transition of Molecular Systems}. Tam, K. M.; Novak, B.; Walker, N.; Moldovan, D.; Jarrell, M. In \textit{APS March Meeting}; 2017.}
        \item {\textbf{Measurement and Calculation of Liquid Ti Alloy Properties with Application to 3D Printing}. Raush, J.; Novak, B.; Zhang, X.; Moldovan, D.; Meng, W.; Guo, S. In \textit{4th World Congress on Integrated Computational Materials Engineering}; 2017.}
        \item {\textbf{Self-Assemblies of Novel Molecules, VECAR}. Shrestha, B.; Kim, H.-Y.; Lee, S.; Novak, B.; Moldovan, D. In \textit{APS March Meeting}; 2015.}
        \item {\textbf{Investigation of Linear Peptide Analogs Self-Assembly and Interaction with DPPC and DPPC/DPPS Lipid Bilayers: A Molecular Dynamics Simulation Study}. Novak, B.; Lin, J.; Moldovan, D. In \textit{The Central and Eastern European Conference on Health and the Environment}; 2014.}
        \item {\textbf{Molecular Dynamics Simulation of Electrically Driven Single DNA Nucleotides through Nanoslits}. Xia, K.; Lin, J.; Nikitopoulos, D.; Moldovan, D. In \textit{ACS Spring National Meeting}; 2013.}
        \item {\textbf{Molecular Dynamics Simulation Study of Bile Salt Aggregation and Interaction with Vitamin E}. Lin, J.; Novak, B.; Moldovan, D. In \textit{ACS Spring National Meeting}; 2013.}
        \item {\textbf{MD Simulation Study of the Effect of Electric Field on the Dynamics of DNA Nucleotides in Hydrophobic Nanoslits}. Xia, K.; Novak, B.; Moldovan, D.; Nikitopoulos, D.; Soper, S. In \textit{ACS Spring National Meeting}; 2012.}
        \item {\textbf{Atomistic Simulation Study of Single DNA Nucleotide Transport through Nanoslits}. Novak, B.; Xia, K.; Nikitopoulos, D.; Soper, S.; Moldovan, D. In ACS Spring National Meeting; 2012.}
        \item {\textbf{Molecular Dynamics Simulation of Adsorption and Positioning of Vitamin E in DMPC Lipid Bilayers: Implication for Their Antioxidant Inhibition}. Novak, B.; Lin, J.; Moldovan, D. In \textit{Colloids and Nanomedicine}; 2012.}
        \item {\textbf{Molecular Dynamics Simulation of Bile Salts Micelle Self-Assembly in Aqueous Solutions}. Lin, J.; Novak, B.; Moldovan, D. In \textit{ACS Spring National Meeting;} 2012.}
        \item {\textbf{Molecular Dynamics Simulation Study of Structural Changes and Pore Formation in Phospholipid Bilayers in the Presence of Dimethylsulfoxide}. Moldovan, D.; Alapati, R.; Novak, B.; Devireddy, R. In \textit{APS March Meeting}; 2010.}
        \item {\textbf{Molecular Dynamics Simulations of the Movement of Single DNA Nucleotides through Nanoslits}. Novak, B.; Xia, K.; Moldovan, D.; Nikitopoulos, D.; Soper, S. In \textit{Southwest \& Southeastern Regional Meeting of the ACS}; 2010.}
        \item {\textbf{Molecular Dynamics Simulation of Self-Assembly of Span80 into Micelles and Their Interaction with Vitamin E}. Lao, J.; Lin, J.; Xia, K.; Sabliov, C.; Moldovan, D. In \textit{Mardi Gras Conference}; 2010.}
        \item {\textbf{Transport of Single Molecules through Nanochannels: A Novel Approach to DNA Sequencing}. Chantiwas, R.; Hupert, M.; Lopez, J.; Datta, P.; Gottert, J.; Novak, B.; Moldovan, D.; Jha, S.; Park, S.; Murphy, M.; et al. In \textit{International Conference on Miniaturized Systems for Chemistry and Life Sciences}; 2009.}
      \end{cvitems}
    }
    
\end{cventries}
