\cvsection{Publications}

\begin{cventries}
  \cventry
    {} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\href{https://doi.org/10.1021/acs.macromol.2c00141}{\textbf{Unraveling the Role of Charge Patterning in the Micellar Structure of Sequence-Defined Amphiphilic Peptoid Oligomers by Molecular Dynamics Simulations}}. Tsai, E.; Gallage Dona, H. K.; Tong, X.; Du, P.; Novak, B.; David, R.; Rick, S. W.; Zhang, D.; Kumar, R. \textit{Macromolecules} 2022, 55, 5197–5212.}
        \item{\href{https://doi.org/10.1021/acs.jpcb.1c09190}{\textbf{Complexation of Lignin Dimers with β-cyclodextrin and Binding Stability Analysis by ESI-MS, Isothermal Titration Calorimetry and Molecular Dynamics Simulations}}. Dean, K.; Novak, B.; Moradipour, M.; Tong, X.; Moldovan, D.; Knutson, B. L.; Rankin, S. E.; Lynn, B. \textit{J. Phys. Chem. B} 2021, 126, 1655–1667.}
        \item{\href{https://www.sciencedirect.com/science/article/abs/pii/S0169433221020705}{\textbf{A Combined Molecular Dynamics/Monte Carlo Simulation of Cu Thin Film Growth on TiN Substrates: Illustration of Growth Mechanisms and Comparison with Experiments}}. Namakian, R.; Novak, B. R.; Zhang, X.; Jin Meng, W.; Moldovan, D. \textit{Appl. Surf. Sci.} 2021, 151013.}
        \item{\href{https://doi.org/10.1116/6.0001029}{\textbf{Interaction of Lignin Dimers with Model Cell Membranes: A Quartz Crystal Microbalance and Molecular Dynamics Simulation Study}}. Moradipour, M.; Tong, X.; Novak, B.; Kamali, P.; Asare, S. O.; Lynn, B. C.; Moldovan, D.; Rankin, S. E.; Knutson, B. L. \textit{Biointerphases} 2021, 16 (4), 041003.}
        \item {\href{https://rdcu.be/clAtY}{\textbf{Molecular Dynamics Simulation Study of the Positioning and Dynamics of α-Tocopherol in Phospholipid Bilayers}}. Kavousi, S.; Novak, B.; Tong, X.; Moldovan, D. \textit{Eur. Biophys. J.} 2021.}
        \item{\href{https://doi.org/10.1016/j.actamat.2021.116885}{\textbf{Quantitative Prediction of Rapid Solidification by Integrated Atomistic and Phase-Field Modeling}}. Kavousi, S.; Novak, B. R.; Moldovan, D.; Asle Zaeem, M. \textit{Acta Mater.} 2021, 211, 116885.}
        \item {\href{https://doi.org/10.1021/acs.jpcb.0c07797}{\textbf{Single Nucleotides Moving Through Nanoslits Composed of Self-Assembled Monolayers via Equilibrium and Nonequilibrium Molecular Dynamics}}. Tong, X.; Novak, B.; Kavousi, S.; Moldovan, D. \textit{J. Phys. Chem. B} 2021, 125 (4), 1259–1270.}
        \item {\href{https://doi.org/10.1016/j.commatsci.2020.109854}{\textbf{Interface Kinetics of Rapid Solidification of Binary Alloys by Atomistic Simulations: Application to Ti-Ni Alloys}}. Kavousi, S.; Novak, B. R.; Hoyt, J.; Moldovan, D. \textit{Comput. Mater. Sci.} 2020, 184, 109854.}
        \item {\href{https://doi.org/10.1021/acs.jpcb.9b05525}{\textbf{Experimental and Molecular Dynamics Simulation Study of the Effects of Lignin Dimers on the Gel-to-Fluid Phase Transition in DPPC Bilayers}}. Tong, X.; Moradipour, M.; Novak, B.; Kamali, P.; Asare, S. O.; Knutson, B. L.; Rankin, S. E.; Lynn, B. C.; Moldovan, D. \textit{J. Phys. Chem. B} 2019, 123 (39), 8247–8260. (\href{https://par.nsf.gov/servlets/purl/10149222}{Open Version})}
        \item {\href{https://doi.org/10.1088/1361-651X/ab580c}{\textbf{Modified Embedded-Atom Method Potential for High-Temperature Crystal-Melt Properties of Ti–Ni Alloys and Its Application to Phase Field Simulation of Solidification}}. Kavousi, S.; Novak, B. R.; Baskes, M. I.; Zaeem, M. A.; Moldovan, D. \textit{Modelling Simul. Mater. Sci. Eng.} 2019, 28 (1), 015006. (\href{https://par.nsf.gov/servlets/purl/10208355}{Open Version})}
        \item {\href{https://doi.org/10.1016/j.enconman.2019.06.070}{\textbf{Rapid Microwave-Assisted Biomass Delignification and Lignin Depolymerization in Deep Eutectic Solvents}}. Muley, P. D.; Mobley, J. K.; Tong, X.; Novak, B.; Stevens, J.; Moldovan, D.; Shi, J.; Boldor, D. \textit{Energy Convers. Manag.} 2019, 196, 1080–1088. (\href{https://www.sciencedirect.com/science/article/am/pii/S0196890419307411}{Open Version})}
        \item {\href{https://doi.org/10.1016/j.commatsci.2019.03.024}{\textbf{Combined Molecular Dynamics and Phase Field Simulation Investigations of Crystal-Melt Interfacial Properties and Dendritic Solidification of Highly Undercooled Titanium}}. Kavousi, S.; Novak, B. R.; Zaeem, M. A.; Moldovan, D. \textit{Comput. Mater. Sci.} 2019, 163, 218–229. (\href{https://ipfs.io/ipfs/QmTY7FGs5p6zrExjUZ5bBpLohWdkmvvgtXZj1JuF9vV8Ay?filename=Combined_molecular_dynamics_and_phase_field_simulation_investigations_of_crystal-melt_interfacial_properties_and_dendritic_solidification_of_highly_undercooled_titanium.pdf}{Open Version})}
        \item {\href{https://doi.org/10.1103/PhysRevE.98.053305}{\textbf{Identifying Structural Changes with Unsupervised Machine Learning Methods}}. Walker, N.; Tam, K.-M.; Novak, B.; Jarrell, M. \textit{Phys. Rev. E} 2018, 98 (5), 053305.}
        \item {\href{https://doi.org/10.1016/j.colsurfa.2017.03.060}{\textbf{The Role of the Asymmetric Bolaamphiphilic Character of VECAR on the Kinetic and Structural Aspects of Its Self-Assembly: A Molecular Dynamics Simulation Study}}. Kim, H.-Y.; Novak, B. R.; Shrestha, B.; Lee, S. E.; Moldovan, D. \textit{Colloids Surf. Physicochem. Eng. Asp.} 2017, 523, 9–18. (\href{https://www.sciencedirect.com/science/article/am/pii/S0927775717303205}{Open Version})}
        \item {\href{https://doi.org/10.1021/acs.jpcb.5b02798}{\textbf{Electrophoretic Transport of Single DNA Nucleotides Through Nanoslits: A Molecular Dynamics Simulation Study}}. Xia, K.; Novak, B. R.; Weerakoon-Ratnayake, K. M.; Soper, S. A.; Nikitopoulos, D. E.; Moldovan, D. \textit{J. Phys. Chem. B} 2015, 119 (35), 11443–11458. }
        \item {\href{https://doi.org/10.1002/9781118462157.ch3}{\textbf{Cellular Fate of Delivery Systems and Entrapped Bioactives}}. Sabliov, C. M.; Moldovan, D.; Novak, B.; Borel, T.; Whaley, M. In Nanotechnology and Functional Foods: Effective Delivery of Bioactive Ingredients; Sabliov, C. M., Chen, H., Yada, R., Eds.; Wiley-Blackwell, 2015; pp 35–51.}
        \item {\href{https://doi.org/10.1021/jp309486c}{\textbf{Distinguishing Single DNA Nucleotides Based on Their Times of Flight through Nanoslits: A Molecular Dynamics Simulation Study}}. Novak, B. R.; Moldovan, D.; Nikitopoulos, D. E.; Soper, S. A. \textit{J. Phys. Chem. B} 2013, 117 (12), 3271–3279. }
        \item {\href{https://doi.org/10.1021/jp208145b}{\textbf{Molecular Dynamics Simulation Study of the Effect of DMSO on Structural and Permeation Properties of DMPC Lipid Bilayers}}. Lin, J.; Novak, B.; Moldovan, D. \textit{J. Phys. Chem. B} 2012, 116, 1299–1308.}
        \item {\href{https://doi.org/10.1002/prot.22910}{\textbf{Behavior of the ATP Grasp Domain of Biotin Carboxylase Monomers and Dimers Studied Using Molecular Dynamics Simulations}}. Novak, B. R.; Moldovan, D.; Waldrop, G. L.; de Queiroz, M. S. \textit{Proteins: Struct. Funct. Bioinform.} 2011, 79, 622–632.}
        \item{\href{https://doi.org/10.1021/jp810650q}{\textbf{Umbrella Sampling Simulations of Biotin Carboxylase: Is a Structure with an Open ATP Grasp Domain Stable in Solution?}} Novak, B. R.; Moldovan, D.; Waldrop, G. L.; de Queiroz, M. S. \textit{J. Phys. Chem. B} 2009, 113 (30), 10097–10103.}
        \item{\href{https://doi.org/10.1115/1.2818771}{\textbf{An Atomistic Simulation Study of the Role of Asperities and Indentations on Heterogeneous Bubble Nucleation}}. Novak, B. R.; Maginn, E. J.; McCready, M. J. \textit{J. Heat Trans.-T. ASME} 2008, 130.}
        \item{\href{https://doi.org/10.1103/PhysRevB.75.085413}{\textbf{Comparison of Heterogeneous and Homogeneous Bubble Nucleation Using Molecular Simulations}}. Novak, B. R.; Maginn, E. J.; McCready, M. J. \textit{Phys. Rev. B} 2007, 75. }
        \item{\href{https://doi.org/10.1023/A:1013966629311}{\textbf{Diffusion and Reactivity of Ruthenium (II) Tris(Bipyridine) and Cobalt (II) Tris(Bipyridine) in Organically Modified Silicates}}. Collinson, M. M.; Novak, B. \textit{J. Sol-Gel Sci. Technol.} 2002, 23, 215–220.}
        \item{\href{https://doi.org/10.1021/ac9913208}{\textbf{Electrochemiluminescence of Ruthenium(II) Tris(Bipyridine) Encapsulated in Sol−Gel Glasses}}. Collinson, M. M.; Novak, B.; Martin, S. A.; Taussig, J. S. \textit{Anal. Chem.} 2000, 72 (13), 2914–2918.}        
      \end{cvitems}
    }
    
%   \cventry
%     {} % Job title
%     {} % Organization
%     {} % Location
%     {} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%       \end{cvitems}
%     }

\end{cventries}
