\pagebreak

\cvsection{Research Experience}

\begin{cventries}
  \cventry
    {Research Associate} % Job title
    {Louisiana State University} % Organization
    {Molecular Simulation} % Location
    {2007/11 - 2021/10} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {\textbf{\underline{Function and dynamics of the enzyme biotin carboxylase}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Showed that the ATP binding domain of biotin carboxylase (BC) is most stable in a closed configuration for a monomer and most stable in an open configuration for a dimer explaining the loss of activity for monomers relative to dimers.}
                \item {Showed that there is communication between monomers of a BC dimer when ATP is bound in one monomer and that the most stable state is one with both monomers closed, supporting other evidence suggesting that a reaction occurs in only one monomer at a time.}
                \end{itemize}
            \item {\textbf{\underline{Sequencing DNA using times-of-flight of single nucleotides as they pass through nanochannels}}}
                \vspace{2pt}
                \begin{itemize}
                    \item {Performed initial simulations in smooth and rough nanoslits composed of a single type of atom in a disordered arrangement approximating polymethyl methacrylate (PMMA).}
                    \item {Assisted graduate students with running simulations with slit walls composed of PMMA and self-assembled monolayers.}
                    \item {Extrapolated simulation results to estimate the slit length required to obtain a given sequencing error rate to compare different surfaces.}
                \end{itemize}        
            \item {\textbf{\underline{Self-assembly of bile salts or cationic linear peptide analogs (LPAs) and their interaction with lipid bilayers}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Showed that LPAs with hydrocarbon connectors longer than 7 carbons form small, stable micelles at high concentrations.}
                \item {Showed that longer LPA hydrocarbon connectors lead to deeper penetration into lipid bilayers.}
                \item {Observed the existence of a long-lived trans-bilayer configuration for LPAs with 11 carbon hydrocarbon connectors.}
                \item {Assisted graduate student and advisor with running bile salt simulations}
                \end{itemize}
            \item {\textbf{\underline{Behavior of alpha-tocopherol (vitamin E) in lipid bilayers}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Performed initial simulations. Assisted graduate student with further simulations.}
                \item {Analyzed trajectory data to show that the higher flip-flop rate of tocopherol at higher concentrations in thinner bilayers such as DMPC is associated with tocopherol clusters that span the bilayer.}
                \end{itemize}
            \item {\textbf{\underline{Interaction of lignin oligomers with lipid bilayers or β-cyclodextrin or microwaves}}}
                \vspace{2pt}
                \begin{itemize}
                    \item {Simulations showed the same qualitative trends as experiments in lipid gel to fluid transition temperatures and lipid/water partition coefficients for three lignin dimer derivatives.}
                    \item {Simulations showed the same qualitative trends in β-cyclodextrin binding affinities as experiments for three lignin dimer derivatives.}
                    \item {Showed that some bonds for lignin in deep eutectic solvents are more susceptible to microwaves including the most common monomer linkage.}
                \end{itemize}            
            % \item {\textbf{\underline{Interaction of poly(lactic-co-glycolic acid) (PLGA) nanoparticles with lipid bilayers}}}
            % \item {span-80}
            \item {\textbf{\underline{Effect of DMSO on lipid bilayers}}}
                \vspace{2pt}
                \begin{itemize}
                    \item Studied the effect of DMSO concentration on water and DMSO bilayer permeabilities, amount of DMSO and water in the bilayer, lipid head group orientations and dynamics, electrostatic potential profile across the bilayer, and numbers of hydrogen bonds involving lipid molecules using simulations with assistance of a graduate student.
                \end{itemize}
            \item {\textbf{\underline{Self-assembly of VECAR (vitamin E-carnosine) bolaamphiphiles}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Assisted collaborators at Southeastern Louisiana University with simulation setup and analysis.}
                \item{Assembly was more elongated \& branched and formed faster with decreasing acyl chain length between the vitamin E \& carnosine ends.}
                \end{itemize}
            \item {\textbf{\underline{Bulk and interfacial properties of molten metals \& alloys}}}
                \vspace{2pt}
                \begin{itemize}
                    \item Computed cohesive energies, densities, diffusivities, pair distribution functions, viscosities, surface tensions and their temperature dependences near the liquidus temperatures for molten Al, Cr, Ni, Ti, Al-Ti, Al-Ni, and Cr-Ni with assistance from REU students
                \end{itemize}
            \item {\textbf{\underline{Parameterization of phase field models for rapid solidification of Ti \& Ti-Ni alloys using molecular dynamics simulations}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Performed simulations to obtain kinetic coefficients for Ti. Assisted graduate student with setup and analysis of other kinetic coefficient and interfacial free energy simulations.}
                \item {Wrote python code to analyze solid-liquid interfacial properties including velocity, interfacial free energy, and concentration profiles.}
                \end{itemize}
            \item {\textbf{\underline{Growth of Cu on TiN}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Assisted graduate student with setup and analysis of simulations which showed that during deposition of Cu on TiN(100), bcc phase grows initially followed by martensitic transformation of bcc to twinned fcc(110).}
                \end{itemize}
            \item {\textbf{\underline{Melting point estimation using unsupervised machine learning}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Assisted collaborators in Physics Department with setup and analysis of simulations.}
                \end{itemize}
            \item {\textbf{\underline{Hybrid continuum/molecular dynamics simulations}}}
                \vspace{2pt}
                \begin{itemize}
                \item {Assisted graduate student with setup and analysis of simulations.}
                \end{itemize}
        \end{cvitems}
    }

  \cventry
    {Graduate Research Assistant} % Job title
    {University of Notre Dame} % Organization
    {Chemical Engineering} % Location
    {2002/08 - 2007/09} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{\underline{Bubble nucleation}}}
            \begin{itemize}
                \item {Showed that 4.5 nm indentations cause a large increase in nucleation rate relative to a smooth surface, but 1.5 nm indentations have little effect}
                \item {Applied a thermodynamic model using Mathematica that explained the location of critical bubble nuclei near flat surfaces and extended this model to geometric surface defects}
            \end{itemize}
      \end{cvitems}
    }
    
  \cventry
    {Undergraduate Research Assistant} % Job title
    {Kansas State University} % Organization
    {Chemistry} % Location
    {1999/01 - 2001/01} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{\underline{Electrochemistry in silica gels}}}
            \begin{itemize}
                \item {Showed the effects of solute-gel interactions by measuring electrochemiluminescence intensities of Ru(bpy)\textsubscript{3}\textsuperscript{2+} and diffusion coefficients of Co(bpy)\textsubscript{3}\textsuperscript{2+} in silica gels and organically modified silica gels}
            \end{itemize}
      \end{cvitems}
    }
    
\end{cventries}
